Explainability and Adversarial Robustness for RNNs

### 2019-12-20 paper/paper.tex
Fixed ARS definition again

We thus propose the \gls{ars} as follows. Let $\mathcal D$ denote the set of distances of adversarial flows from original flows, assigning unsuccessful samples a distance of $\infty$, $N = | \mathcal D | \in \mathbb N$ the total number of samples and $Q_{0.5}(\cdot)$ the median function.
We define the \gls{ars} as 
\begin{equation}
\text{ARS} = \frac{1}{\lceil N/2 \rceil} \sum\nolimits_{d \in \tilde {\mathcal D}} d,
\end{equation}
with $\tilde {\mathcal D} \subset \mathcal D$ denoting the set of size $|\tilde {\mathcal D}| =\lceil N/2 \rceil$, so that for all $d \in  \tilde {\mathcal D}, d \le Q_{0.5}(\mathcal D)$.
The \gls{ars} is thus approximately the average of distances smaller than or equal to the median distance.

>>>>

We thus propose the \gls{ars} as follows. Let $\mathcal S$ denote the set of samples, $N = | \mathcal S | \in \mathbb N$ the total number of samples and $d_s \in \mathbb R_0^+$ the distance of an adversarial flow from the original flow for a sample $s\in \mathcal S$, assigning unsuccessful samples a distance of $\infty$. % and $Q_{0.5}(\cdot)$ the median function.
We define the \gls{ars} as 
\begin{equation}
\text{ARS} = \frac{1}{\lceil N/2 \rceil} \sum\nolimits_{\tilde s \in \tilde {\mathcal S}} d_{\tilde s},
\end{equation}
with $\tilde {\mathcal S} \subset \mathcal S$ denoting a set of size $|\tilde {\mathcal S}| =\lceil N/2 \rceil$, so that $d_{\tilde s} \le d_s$ for all $\tilde s \in  \tilde {\mathcal S}, s \in   {\mathcal S} \setminus \tilde {\mathcal S} $.
% We thus propose the \gls{ars} as follows. Let $\mathcal D$ denote the set of distances of adversarial flows from original flows, assigning unsuccessful samples a distance of $\infty$, $N = | \mathcal D | \in \mathbb N$ the total number of samples and $Q_{0.5}(\cdot)$ the median function.
% We define the \gls{ars} as 
% \begin{equation}
% \text{ARS} = \frac{1}{\lceil N/2 \rceil} \sum\nolimits_{d \in \tilde {\mathcal D}} d,
% \end{equation}
% with $\tilde {\mathcal D} \subset \mathcal D$ denoting the set of size $|\tilde {\mathcal D}| =\lceil N/2 \rceil$, so that for all $d \in  \tilde {\mathcal D}, d \le Q_{0.5}(\mathcal D)$.
The \gls{ars} is thus approximately the average of distances not larger than the median distance.
